\Large{Learning to Pivot with Adversarial Networks}

### 2016-10-31 tex/paper.tex
typo

\begin{figure*}
    \begin{center}
        \includegraphics[width=0.245\textwidth]{figures/f-plain.pdf}
        \includegraphics[width=0.245\textwidth]{figures/surface-plain.pdf}
        \includegraphics[width=0.245\textwidth]{figures/f-adversary.pdf}
        \includegraphics[width=0.245\textwidth]{figures/surface-adversary.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{Toy example.
    (Left) Conditional probability densities of the decision scores at $Z=-\sigma, 0, \sigma$
       when $f$ is built without adversarial training. The resulting densities
       are clearly dependent on the continuous parameter $Z$, indicating that $f$ is not pivotal.
    (Middle left) The corresponding decision surface, highlighting
       the fact that samples are easier to classify for values of $Z$ above to $\sigma$,
       hence partially explaining the dependency.
    (Middle right) Conditional probability densities of the decision scores at $Z=-\sigma, 0, \sigma$ when $f$ is
       built with adversarial training, as outlined in Section~\ref{sec:method}.
       The resulting densities are now almost identical to each other, indicating only a
       small dependency on $Z$.
    (Right) The corresponding decision surface, illustrating how adversarial
       training bends the decision function vertically to erase the dependency on $Z$.
    }
    \label{fig:toy}
\end{figure*}

>>>>

\begin{figure*}
    \begin{center}
        \includegraphics[width=0.245\textwidth]{figures/f-plain.pdf}
        \includegraphics[width=0.245\textwidth]{figures/surface-plain.pdf}
        \includegraphics[width=0.245\textwidth]{figures/f-adversary.pdf}
        \includegraphics[width=0.245\textwidth]{figures/surface-adversary.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{Toy example.
    (Left) Conditional probability densities of the decision scores at $Z=-\sigma, 0, \sigma$
       when $f$ is built without adversarial training. The resulting densities
       are clearly dependent on the continuous parameter $Z$, indicating that $f$ is not pivotal.
    (Middle left) The corresponding decision surface, highlighting
       the fact that samples are easier to classify for values of $Z$ above $\sigma$,
       hence partially explaining the dependency.
    (Middle right) Conditional probability densities of the decision scores at $Z=-\sigma, 0, \sigma$ when $f$ is
       built with adversarial training, as outlined in Section~\ref{sec:method}.
       The resulting densities are now almost identical to each other, indicating only a
       small dependency on $Z$.
    (Right) The corresponding decision surface, illustrating how adversarial
       training bends the decision function vertically to erase the dependency on $Z$.
    }
    \label{fig:toy}
\end{figure*}
